Lower Bounds on the Minimax Risk for the \\ Source Localization Problem

### 2017-05-07 paper.tex
Make all edits permanent; fix paper length.

@@

\author{
	\IEEEauthorblockN{
		Praveen Venkatesh (\href{mailto:vpraveen@cmu.edu}{\texttt{vpraveen@cmu.edu}}) %\IEEEauthorrefmark{1}
		and Pulkit Grover (\href{mailto:pulkit@cmu.edu}{\texttt{pulkit@cmu.edu}}) %\IEEEauthorrefmark{2}
	}
	\IEEEauthorblockA{
		\textcolor{red}{Electrical \& Computer Engineering,
		and the Center for the Neural Basis of Cognition,
		Carnegie Mellon University}
		%\\
		%\IEEEauthorrefmark{1}\href{mailto:vpraveen@cmu.edu}{\texttt{vpraveen@cmu.edu}}
		%\IEEEauthorrefmark{2}\href{mailto:pulkit@cmu.edu}{\texttt{pulkit@cmu.edu}}
	}
}

@@

This paper seeks to address the shortcomings of earlier methods by deriving
lower bounds on the minimax risk for the source localization problem, which
apply to \emph{all} estimators (biased \emph{and} unbiased), and which capture
how the bound scales with increasing numbers of sensors. Previous lower bounds
are based on ``spherical head
models''~\cite{Nunez2006Electric,Grover2016Information}, which admit analytical
solutions for the potential of a single dipole. But spherical models are not
easily amenable to analytical lower bounds which seek to capture scaling in the
number of sensors, because the spherical surface does not permit uniform
sampling~\cite{Heath1956Thirteen}. We therefore restrict our analysis to a
source localization problem on a one-dimensional ``circular'' domain (to be
described in detail in Section~\ref{sec:source-localization}).
\textcolor{red}{While this simplified model makes crucial assumptions (such as
	shift-invariance) that are invalid in more realistic brain models, we hope
	that the techniques presented here will pave the way for deriving numerical
	bounds in more complex settings.}

@@

Hence, we believe that this paper is the first to give lower bounds on the
minimax error in estimating the location of a point source, which is observed
by sensors through a diffusive medium, and corrupted by additive white Gaussian
noise. We are also the first to analyze the implications physical sensor models
have on such lower bounds. A simplistic theoretical model might assume that the
number of sensors can increase unbounded, while maintaining a fixed SNR at each
sensor. We show that this is not physically possible in our setting, and derive
numerical bounds which have radically different asymptotic behaviour.

We describe the problem setting in Section~\ref{sec:source-localization} and
the minimax techniques and our main results (for a na\"ive and then for a more
physical sensor model) in Section~\ref{sec:minimax-lower-bounds}. We conclude
in Section~\ref{sec:discussion} with a discussion on the goodness of our
bounds, and on how our results can be extended to other settings.

@@

\section{\textcolor{red}{The source localization problem} \textcolor{green}{Source Localization in 1D}}
\label{sec:source-localization}

\textcolor{red}{\sout{We start by giving a detailed description of the one-dimensional setting of the
source localization problem.}}

@@

We assume that the point source is located on a circle of circumference $S$. We
use the variable `$s$' (for \emph{s}pace) to represent a general point on this
domain. We can also view this domain as a line, on which signals are periodic
with period $S$.  The point source is therefore located somewhere within one
period. We denote the set of possible locations by $\Theta = [0, S)$.
\textcolor{red}{\sout{Due to
the periodic nature of the domain, a source located at position $\theta \in
\Theta$ implies the presence of sources at $s = \theta + kS$,~$\forall \, k \in
\mathbb Z$.}}

@@

Sensors are assumed to be uniformly distributed over the domain, i.e., if there
are $m$ sensors, they are placed at locations $s = 0$, $S/m$, $2S/m$,~\dots,
$(m{-}1)S/m$ (the offset of the first sensor is arbitrary, so without loss of
generality we take it to be 0). \textcolor{red}{\sout{The periodicity of the space ensures that we
automatically also have sensors at $S$, $S{+}S/m$,~\dots\@}} The lower bounds we
provide are for \emph{this specific sensor configuration}. For a discussion on
why this configuration might be an appropriate choice in the minimax setting,
see section~\ref{sec:discussion}.

@@

All ``continuous-space'' signals (analogous to continuous- and
discrete-\emph{time} signals) on the aforementioned circular domain are of the
form $f:\Theta\mapsto\mathbb{R}$.  The point source located at $\theta$ is
represented by the impulse signal, $f(s;\theta) = \delta(s - \theta)$, where
$\delta(\cdot)$ is the Dirac delta function.  The sensors observe this signal
through the diffusive medium, which, intuitively speaking, blurs the impulse.
More concretely, we assume that the medium is linear and shift-invariant, so
that it can be \textcolor{red}{characterized} by a spatial impulse response.
Then, blurring would correspond to low-pass filtering.  Let this impulse
response be given by $g(s)$. Then, the noiseless, continuous-space signal
(post-filtering and pre-sampling) is given by the convolution, $x(s; \theta) =
(g*f)(s) = g(s - \theta)$. Here, we further make the simplifying assumption
that $g(s)$ has a sufficiently restricted support, so that aliasing effects are
avoided, and $x(s; \theta)$ is always well-defined. To be precise, $g(s) = 0$
when $\abs{s} > w/2$, where the ``width'' $w$ of the impulse response satisfies
$w < S / 2$ (the reason for the extra factor of $1/2$ will become clear in a
later section). For the proof, $g(s)$ is also assumed to be Lipschitz
continuous with parameter $\kappa$, i.e., $\abs{g(u) - g(v)} \leq \kappa \abs{u
- v} \; \forall \;\; u, v \in \Theta$.

@@

\begin{figure}[tp] %  figure placement: here, top, bottom, or page
	\centering
	\includegraphics[width=3.2in]{block-diagram}
	\caption{A block diagram of the two sensor models described in
	section~\ref{sec:signal-model}.}
	\label{fig:signal-model}
\end{figure}

@@

We start by lower bounding the maximum risk of the estimation problem with the
average risk of a multiple hypothesis testing problem. For this, we first need
to define a $2\delta$-packing.%
\begin{definition}
	A set $\Theta_{\mathcal{V}} = \{ \theta_v : v \in \mathcal{V} \}$ for some
	finite index set $\mathcal{V} \subset \mathbb N$ is said to be a
	$2\delta$-packing in the $\rho$-metric if
	\begin{equation}
		\rho(\theta_i, \theta_j) \geq 2\delta \qquad \forall \;\; \theta_i, \theta_j \in \Theta_{\mathcal{V}}.
	\end{equation}
\end{definition}
\begin{theorem} \label{thm:est-to-testing}%
	If we can find a $2\delta$-packing $\Theta_{\mathcal{V}}$ of $\Theta$, then
	we can lower bound the minimax estimation risk by the average testing risk:
	\begin{equation}
		\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \Phi(\delta) \inf_\psi \mathbb P (\psi(Y^n) \neq V)
	\end{equation}
	where $V$ is the unknown true hypothesis which takes values uniformly from
	$\mathcal{V}$, and $\psi$ is our estimate of the hypothesis.
\end{theorem}
\textcolor{red}{For a proof of this theorem, we refer the reader
to~\cite[Sec.~2.2]{Tsybakov2009Introduction}, or
to~\cite[Prop.~13.3]{Duchi2015Information}}. Intuitively,
Theorem~\ref{thm:est-to-testing} says that the error in estimating $\theta_i$
is likely to be large if it is difficult to distinguish $\theta_i$ from
$\theta_j$, i.e.\ if the probability of error is high.

We now need to lower bound the probability of error in the hypothesis testing
problem. The simplest way to do this is to consider a binary hypothesis test
and use what is known as Le Cam's method:
\begin{theorem} \label{thm:le-cam}
	For a binary hypothesis test, i.e., $\mathcal{V} = \{0, 1\}$,
	\begin{equation}
		\inf_\psi \mathbb P(\psi(Y^n) \neq V) = 1 - \norm{P_0 - P_1}_{TV}
	\end{equation}
	where $P_i$ is short-hand for $P(\theta_i)$ and $\norm{P_0 - P_1}_{TV}$ is
	the total variation distance between the two distributions, defined as
	$\norm{\cdot}_{TV} = \frac{1}{2} \norm{\cdot}_1$.
\end{theorem}
\textcolor{red}{For a proof, we refer the reader to~\cite[Thm.~2.2]{Tsybakov2009Introduction},
or to~\cite[Prop.~2.11]{Duchi2015Information} for a more readable account.}
Intuitively, Theorem~\ref{thm:le-cam} states that the minimum achievable error
probability in a binary hypothesis testing problem is related to the distance
between the distributions corresponding to the two hypotheses.

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=2.6in]{overlap-middle-pics}
	\caption{Depiction of the continuous-space signals produced by two
		hypotheses, $\theta_0$ and $\theta_1$. Note that each signal is a
		shifted impulse response, and therefore has a support of size $w$.
		The set $\{\theta_0, \theta_1\}$ is a $2\delta$-packing of
		$\Theta$, so the signals are separated by a distance $2\delta$.}
	\label{fig:overlap-middle}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=2.6in]{delta-sampled-pics}
	\caption{Plot of the samples of the difference signal, $\Delta(k)$. The
		total size of the support of the difference signal is $w+2\delta$,
		hence at most $\floor*{\frac{(w + 2\delta)m}{S} + 1}$ samples of
		$\Delta(k)$ are non-zero.}
	\label{fig:delta-sampled}
\end{figure}

@@

inequality~\cite{Kullback1967Lower} and the convenient tensorization of the
KL-divergence~\cite{Duchi2015Information}, we see that:

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=2.8in]{lb-vs-m-annotated}
	\caption{A numerically generated plot of the lower bound on minimax risk of
		source localization, against the number of uniformly distributed
		sensors, $m$, used to estimate the location (code available
		online~\cite{Code}). The different curves are for different numbers of
		``trials'', $n$ (number of i.i.d.\ sensor observations). The bound
		saturates for large $m$, indicating that for a \emph{fixed} number of
		trials, there is decreasing benefit to using more sensors.  However,
		the plot suggests that with more trials, the bound saturates at
		increasingly larger numbers of sensors. Thus, there may be benefit to
		increasing the number of sensors when you have more trials.}
	\label{fig:numerical}
\end{figure}

@@

While the lower bound presented in section~\ref{sec:lecam-lb} is non-physical
for a large number of sensors, it still gives some important insights.
\textcolor{red}{\sout{For instance, if we assume that sensors have a constant
		width $c$, then even if we view sensors as integrators, the bound tells
		us something about the scaling of error with number of sensors, up to
		$m = \floor*{\frac{S}{c}}$.} The bound tells us how the error scales
	with the number of sensors up to $m = \floor*{\frac{S}{c}}$, for sensors of
	a constant width $c$.} \textcolor{red}{\sout{Beyond this point, averaging
		noise by increasing the number of trials may help one get to a target
		mean squared error in location.} Averaging noise over a larger number
	of trials $n$ may help one achieve a target mean squared error in
	location}. An analytical derivation of the trade-off between $m$ and $n$ in
achieving a certain target MSE is relegated to future work. \textcolor{red}{Further, more sophisticated techniques for deriving lower bounds, such as Fano's method~\cite[Sec.~2.7.1]{Tsybakov2009Introduction} are yet to be analyzed.}

@@

While the bounds in section~\ref{sec:lecam-lb} were derived for a
one-dimensional circular domain, extensions to a 1D linear domain (of fixed
length $S$) and to a $d$-dimensional domain (circular or linear) are fairly
straightforward, under certain conditions. For a 1D linear domain, we require
that sensors capture the entirety of the impulse response even at the edges of
the domain. Hence, sensors must be placed uniformly in $[-w/2, S{+}w/2]$. For
extending to $d$ dimensions, it suffices to apply Assouad's
Lemma~\cite[Sec.~2.7.2]{Tsybakov2009Introduction} to separate the problem into
$d$ independent 1D problems. Such extensions substantially broaden the
\textcolor{red}{\sout{number of settings in which this bound applies.}
	application domains where this bound could be useful.}

@@

\section*{Acknowledgements}

\textcolor{red}{The authors thank Prof.\ Aarti Singh for her useful comments on
	a preliminary draft of this paper.}
\textcolor{blue}{
This work was supported in part by Systems on Nanoscale Information fabriCs
(SONIC), one of the six SRC STARnet Centers, sponsored by MARCO and DARPA.
Praveen Venkatesh was supported (in part) by the Dowd Fellowship from the
College of Engineering at Carnegie Mellon University. The authors would like to
thank Philip and Marsha Dowd for their financial support and encouragement.
}

@@

\newpage

>>>>

\IEEEoverridecommandlockouts

@@

\author{
	\IEEEauthorblockN{
		Praveen Venkatesh (\href{mailto:vpraveen@cmu.edu}{\texttt{vpraveen@cmu.edu}}) %\IEEEauthorrefmark{1}
		and Pulkit Grover (\href{mailto:pulkit@cmu.edu}{\texttt{pulkit@cmu.edu}}) %\IEEEauthorrefmark{2}
	}
	\IEEEauthorblockA{
		Electrical \& Computer Engineering,
		and the Center for the Neural Basis of Cognition,
		Carnegie Mellon University
		%\\
		%\IEEEauthorrefmark{1}\href{mailto:vpraveen@cmu.edu}{\texttt{vpraveen@cmu.edu}}
		%\IEEEauthorrefmark{2}\href{mailto:pulkit@cmu.edu}{\texttt{pulkit@cmu.edu}}
	}
	\thanks{This work was supported in part by Systems on Nanoscale
	Information fabriCs (SONIC), one of the six SRC STARnet Centers, sponsored
	by MARCO and DARPA.  Praveen Venkatesh was supported (in part) by the Dowd
	Fellowship from the College of Engineering at Carnegie Mellon University.
	The authors would like to thank Philip and Marsha Dowd for their financial
	support and encouragement. The authors thank Prof.\ Aarti Singh for her
	useful comments on a preliminary draft of this paper.
	}
	\vspace{-0.25in}
}

@@

This paper seeks to address the shortcomings of earlier methods by deriving
lower bounds on the minimax risk for the source localization problem, which
apply to \emph{all} estimators (biased \emph{and} unbiased), and which capture
how the bound scales with increasing numbers of sensors. Previous lower bounds
are based on ``spherical head
models''~\cite{Nunez2006Electric,Grover2016Information}, which admit analytical
solutions for the potential of a single dipole. But spherical models are not
easily amenable to analytical lower bounds which seek to capture scaling in the
number of sensors, because the spherical surface does not permit uniform
sampling~\cite{Heath1956Thirteen}. We therefore restrict our analysis to a
source localization problem on a one-dimensional ``circular'' domain (to be
described in detail in Section~\ref{sec:source-localization}).  While this
simplified model makes crucial assumptions (such as shift-invariance) that are
invalid in more realistic brain models, we hope that the techniques presented
here will pave the way for deriving numerical bounds in more complex settings.

@@

Hence, we believe that this paper is the first to give lower bounds on the
minimax error in estimating the location of a point source observed by sensors
through a diffusive medium, and corrupted by additive white Gaussian noise. We
are also the first to analyze the implications of physical sensor models on
such lower bounds. A simplistic theoretical model might assume that the number
of sensors can increase unbounded, while maintaining a fixed SNR at each
sensor. We show that this is not physically possible in our setting, and derive
numerical bounds which have very different asymptotic behaviour.

We describe the problem setting in Section~\ref{sec:source-localization} and
the minimax techniques and our main results in
Section~\ref{sec:minimax-lower-bounds}. We conclude in
Section~\ref{sec:discussion} with a discussion on the goodness of our bounds,
and on possible extensions.

@@

\section{Source Localization in 1D}
\label{sec:source-localization}

@@

We assume that the point source is located on a circle of circumference $S$. We
use the variable `$s$' (for \emph{s}pace) to represent a general point on this
domain. We can also view this domain as a line, on which signals are periodic
with period $S$.  The point source is therefore located somewhere within one
period. We denote the set of possible locations by $\Theta = [0, S)$.

@@

Sensors are assumed to be uniformly distributed over the domain, i.e., if there
are $m$ sensors, they are placed at locations $s = 0$, $S/m$, $2S/m$,~\dots,
$(m{-}1)S/m$ (the offset of the first sensor is arbitrary, so without loss of
generality we take it to be 0). The lower bounds we provide are for \emph{this
	specific sensor configuration}. For a discussion on why this configuration
might be an appropriate choice in the minimax setting, see
section~\ref{sec:discussion}.

@@

All ``continuous-space'' signals (analogous to continuous- and
discrete-\emph{time} signals) on the aforementioned circular domain are of the
form $f:\Theta\mapsto\mathbb{R}$.  The point source located at $\theta$ is
represented by the impulse signal, $f(s;\theta) = \delta(s - \theta)$, where
$\delta(\cdot)$ is the Dirac delta function.  The sensors observe this signal
through the diffusive medium, which, intuitively speaking, blurs the impulse.
More concretely, we assume that the medium is linear and shift-invariant, so
that it can be characterized by a spatial impulse response.  Then, blurring
would correspond to low-pass filtering.  Let this impulse response be given by
$g(s)$. Then, the noiseless, continuous-space signal (post-filtering and
pre-sampling) is given by the convolution, $x(s; \theta) = (g*f)(s) = g(s -
\theta)$. Here, we further make the simplifying assumption that $g(s)$ has a
sufficiently restricted support, so that aliasing effects are avoided, and
$x(s; \theta)$ is always well-defined. To be precise, $g(s) = 0$ when $\abs{s}
> w/2$, where the ``width'' $w$ of the impulse response satisfies $w < S / 2$
(the reason for the extra factor of $1/2$ will become clear in a later
section). For the proof, $g(s)$ is also assumed to be Lipschitz continuous with
parameter $\kappa$, i.e., $\abs{g(u) - g(v)} \leq \kappa \abs{u - v} \; \forall
\;\; u, v \in \Theta$.

@@

\begin{figure}[tp] %  figure placement: here, top, bottom, or page
	\centering
	\includegraphics[width=3.2in]{block-diagram}
	\vspace{-3pt}
	\caption{A block diagram of the two sensor models described in
	section~\ref{sec:signal-model}.}
	\label{fig:signal-model}
\end{figure}

@@

We start by lower bounding the maximum risk of the estimation problem with the
average risk of a multiple hypothesis testing problem. For this, we first need
to define a $2\delta$-packing.%
\begin{definition}
	A set $\Theta_{\mathcal{V}} = \{ \theta_v : v \in \mathcal{V} \}$ for some
	finite index set $\mathcal{V} \subset \mathbb N$ is said to be a
	$2\delta$-packing in the $\rho$-metric if
	\begin{equation}
		\rho(\theta_i, \theta_j) \geq 2\delta \qquad \forall \;\; \theta_i, \theta_j \in \Theta_{\mathcal{V}}.
	\end{equation}
\end{definition}
\begin{theorem} \label{thm:est-to-testing}%
	If we can find a $2\delta$-packing $\Theta_{\mathcal{V}}$ of $\Theta$, then
	we can lower bound the minimax estimation risk by the average testing risk:
	\begin{equation}
		\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \Phi(\delta) \inf_\psi \mathbb P (\psi(Y^n) \neq V)
	\end{equation}
	where $V$ is the unknown true hypothesis which takes values uniformly from
	$\mathcal{V}$, and $\psi$ is our estimate of the hypothesis.
\end{theorem}
For a proof of this theorem, we refer the reader
to~\cite[Sec.~2.2]{Tsybakov2009Introduction}, or
to~\cite[Prop.~13.3]{Duchi2015Information}. Intuitively,
Theorem~\ref{thm:est-to-testing} says that the error in estimating $\theta_i$
is likely to be large if it is difficult to distinguish $\theta_i$ from
$\theta_j$, i.e.\ if the probability of error is high.

We now need to lower bound the probability of error in the hypothesis testing
problem. The simplest way to do this is to consider a binary hypothesis test
and use what is known as Le Cam's method:
\begin{theorem} \label{thm:le-cam}
	For a binary hypothesis test, i.e., $\mathcal{V} = \{0, 1\}$,
	\begin{equation}
		\inf_\psi \mathbb P(\psi(Y^n) \neq V) = 1 - \norm{P_0 - P_1}_{TV}
	\end{equation}
	where $P_i$ is short-hand for $P(\theta_i)$ and $\norm{P_0 - P_1}_{TV}$ is
	the total variation distance between the two distributions, defined as
	$\norm{\cdot}_{TV} = \frac{1}{2} \norm{\cdot}_1$.
\end{theorem}
For a proof, we refer the reader to~\cite[Thm.~2.2]{Tsybakov2009Introduction},
or to~\cite[Prop.~2.11]{Duchi2015Information} for a more readable account.
Intuitively, Theorem~\ref{thm:le-cam} states that the minimum achievable error
probability in a binary hypothesis testing problem is related to the distance
between the distributions corresponding to the two hypotheses.

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=2.6in]{overlap-middle-pics}
	\vspace{-3pt}
	\caption{Depiction of the continuous-space signals produced by two
		hypotheses, $\theta_0$ and $\theta_1$. Note that each signal is a
		shifted impulse response, and therefore has a support of size $w$.
		The set $\{\theta_0, \theta_1\}$ is a $2\delta$-packing of
		$\Theta$, so the signals are separated by a distance $2\delta$.}
	\label{fig:overlap-middle}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=2.6in]{delta-sampled-pics}
	\vspace{-3pt}
	\caption{Plot of the samples of the difference signal, $\Delta(k)$. The
		total size of the support of the difference signal is $w+2\delta$,
		hence at most $\floor*{\frac{(w + 2\delta)m}{S} + 1}$ samples of
		$\Delta(k)$ are non-zero.}
	\label{fig:delta-sampled}
\end{figure}

@@

inequality~\cite[Lemma~2.5]{Tsybakov2009Introduction} and the convenient
tensorization of the KL-divergence~\cite{Duchi2015Information}, we see that:

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=2.8in]{lb-vs-m-annotated}
	\vspace{-3pt}
	\caption{A numerically generated plot of the lower bound on minimax risk of
		source localization, against the number of uniformly distributed
		sensors, $m$, used to estimate the location (code available
		online~\cite{Code}). The different curves are for different numbers of
		``trials'', $n$ (number of i.i.d.\ sensor observations). The bound
		saturates for large $m$, indicating that for a \emph{fixed} number of
		trials, there is decreasing benefit to using more sensors.  However,
		the plot suggests that with more trials, the bound saturates at
		increasingly larger numbers of sensors. Thus, there may be benefit to
		increasing the number of sensors when you have more trials.}
	\label{fig:numerical}
\end{figure}

@@

While the lower bound presented in section~\ref{sec:lecam-lb} is non-physical
for a large number of sensors, it still gives some important insights.  The
bound tells us how the error scales with the number of sensors up to $m =
\floor*{\frac{S}{c}}$, for sensors of a constant width $c$. Averaging noise
over a larger number of trials $n$ may help one achieve a target mean squared
error in location. An analytical derivation of the trade-off between $m$ and
$n$ in achieving a certain target MSE is relegated to future work. Further,
more sophisticated techniques for deriving lower bounds, such as Fano's
method~\cite[Sec.~2.7.1]{Tsybakov2009Introduction} are yet to be analyzed.

@@

While the bounds in section~\ref{sec:lecam-lb} were derived for a
one-dimensional circular domain, extensions to a 1D linear domain (of fixed
length $S$) and to a $d$-dimensional domain (circular or linear) are fairly
straightforward, under certain conditions. For a 1D linear domain, we require
that sensors capture the entirety of the impulse response even at the edges of
the domain. Hence, sensors must be placed uniformly in $[-w/2, S{+}w/2]$. For
extending to $d$ dimensions, it suffices to apply Assouad's
Lemma~\cite[Sec.~2.7.2]{Tsybakov2009Introduction} to separate the problem into
$d$ independent 1D problems. Such extensions substantially broaden the
application domains where this bound could be useful.

@@

%\section*{Acknowledgments}

%This work was supported in part by Systems on Nanoscale Information fabriCs
%(SONIC), one of the six SRC STARnet Centers, sponsored by MARCO and DARPA.
%Praveen Venkatesh was supported (in part) by the Dowd Fellowship from the
%College of Engineering at Carnegie Mellon University.
%The authors thank Prof.\ Aarti Singh for her useful comments on a preliminary
%draft of this paper.
%The authors would like to thank Philip and Marsha Dowd for their financial
%support and encouragement.

@@

%\newpage
